\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-09-02 lang-design.tex
Save.

Inspired by the above challenges and Family Polymorphism, we propose
the following extension to Coq's Vernacular Commands, and the corresponding STLC example.
% basically write down the specification of surface Coq commandline
%   and then explain  how the language design makes the programmer’s life easier
\begin{align*}
  V := \quad &"Family"~\langle ident\rangle~["extends"~\langle ident\rangle] 
  \quad |\quad "EndFamily" \quad | \quad "SealFamily" \\
  & |\quad "FRecursor"~\langle ident\rangle~"about"~\langle ident\rangle~"motive"~\langle term\rangle~"using"~\langle ident\rangle \\
  & | \quad "FTheorem"~\langle ident\rangle~"about"~\langle ident\rangle~"motive"~\langle term\rangle \\
  & |\quad ["Extend" | "Override"]~"Family"~\langle ident\rangle \\ 
  & |\quad ["Extend"]~"FInductive"~\langle ident\rangle \\ 
  & |\quad ["Final" | "Override"]~"Field"~\langle ident\rangle~":"~\langle term \rangle~":="~\langle term \rangle \\
  & | \quad "FieldClaim"~\langle ident\rangle~":"~\langle term \rangle \\
  & | \quad "Inherit"~\langle ident\rangle \quad | \quad "Inherit Until"~\langle ident\rangle \quad \\
  & | \quad "Closing Fact"~\langle ident\rangle~":"~\langle term \rangle~":="~\langle term \rangle \\ 
  & | \quad "Closing Fact"~\langle ident\rangle~":"~\langle term \rangle~"by"~"\{"\langle \text{one tactic expression}\rangle"\}" \\ 
  & | \quad "MetaData"~\langle ident\rangle \quad | \quad "EndMetaData" \\ 
\end{align*}

@@

@@

@@

We will explain the usage of "Closing Fact" and "MetaData" later---they are here to resolve \ref{chg:software-engineering} to some extent.
% This incomplete support can already be useful for extending functions.
% Take \cref{fig:plugin-example2} as example, if we want to extend boolean
% inductive type and its negation, we only need to specify the new
% constructor for boolean and how negation deals with the new constructor.
% As a result, the programmer does not have to duplicate code---otherwise
% the user will need to copy and paste the whole original negation
% definition and add a new pattern matching case.

>>>>

Inspired by the above challenges and Family Polymorphism, we propose
the following extension to Coq's Vernacular Commands, and the corresponding STLC example.
% basically write down the specification of surface Coq commandline
%   and then explain  how the language design makes the programmer’s life easier
\begin{align*}
  V := \quad &"Family"~\langle ident\rangle~["extends"~\langle ref\rangle] 
  \quad |\quad "EndFamily" \quad | \quad "SealFamily" \\
  & |\quad "FRecursor"~\langle ident\rangle~"about"~\langle ref\rangle~"motive"~\langle term\rangle~"using"~\langle ref\rangle \\
  & |\quad "FScheme CompEq about"~\langle ref \rangle~|\quad "FScheme " \langle ident\rangle " PRecT about"~\langle ref \rangle\\
  & | \quad "FTheorem"~\langle ident\rangle~"about"~\langle ident\rangle~"motive"~\langle term\rangle \\
  & |\quad ["Extend"]~"Family"~\langle ident\rangle \\ 
  & |\quad ["Extend"]~"FInductive"~\langle ident\rangle \\ 
  & |\quad ["Overridable " ["pins " \{ \langle ident\rangle ... \}]]~"Field"~\langle ident\rangle~":"~\langle term \rangle~":="~\langle term \rangle \\
  & |\quad ["Override"]~"Field"~\langle ident\rangle~":"~\langle term \rangle~":="~\langle term \rangle \\
  & | \quad "FieldClaim"~\langle ident\rangle~":"~\langle term \rangle \\
  & | \quad "Inherit"~\langle ident\rangle \quad | \quad "Inherit Until"~\langle ident\rangle \quad \\
  & | \quad "Closing Fact"~\langle ident\rangle~":"~\langle term \rangle~":="~\langle term \rangle \\ 
  & | \quad "Closing Fact"~\langle ident\rangle~":"~\langle term \rangle~"by"~"\{"\langle \text{one tactic expression}\rangle"\}" \\ 
  & | \quad "Family"~\langle ident\rangle~"extends"~\langle ref\rangle~"using"~\langle ref\rangle~"using"~\langle ref\rangle \\ 
  & | \quad "MetaData"~\langle ident\rangle \quad | \quad "EndMetaData" \\ 
\end{align*}

@@

Unlike how Coq's "Inductive" will automatically generate the eliminator for the inductive type, we require the user to explicit use "FScheme .. PRecT" to generate a \textit{partial recursor} for the "FInductive". We will later explain what a partial recursor is, at this point the reader can just consider it as a mundane eliminator.

@@

% Explain FScheme
However, "FRecursor" doesn't specify any reduction/computation information until a family is defined completely and closed (e.g. "subst" in \cref{fig:STLC-example2} cannot reduce when application during the definition of the surrounding family). To remedy this, we introduce "FScheme CompEq" that will generate proposition of equations indicating reductions. For example, for "subst", it will generate the equation
\mintinline{Coq}{subst tm_unit = subst_internal.tm_unit}.

Similarly, the generated partial recursor using "FScheme .. PRecT" doesn't have computation information either, and require "FScheme CompEq" to generate them.

% Explain Mixin

\textbf{Mixin.} For two inheritance with the same parent family, we support mixin the two using "Family ... extends ... using ... using ...". However, the candidates for mixin cannot have any overriding term (i.e. only allow inheritance and extension).

@@

We will explain the usage of "Closing Fact" and "MetaData" later---they are \textit{escape-hatches} to resolve \ref{chg:software-engineering} to some extent.
% This incomplete support can already be useful for extending functions.
% Take \cref{fig:plugin-example2} as example, if we want to extend boolean
% inductive type and its negation, we only need to specify the new
% constructor for boolean and how negation deals with the new constructor.
% As a result, the programmer does not have to duplicate code---otherwise
% the user will need to copy and paste the whole original negation
% definition and add a new pattern matching case.
